Influences on the access to higher education: Visualization and modeling for Chilean data

### 2021-10-09 Paper_Higher_Education.Rmd
Add files via upload

Fig_7 <- ggplot(as.data.frame(Alluvial),
       aes(y = N, axis1 = COD_DEPE2, axis2=TIPO_INST_3)) +
  geom_alluvium(aes(fill = COD_DEPE2), width = 1/12) +
  geom_stratum(width = 1/12, fill = "black", color = "grey") +
  geom_label(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Dependence","Institution"), expand = c(.05, .05)) +
  scale_fill_brewer(type = "qual", palette = "Set1") + labs(y="Graduates Enrolled", fill="Dependence") +
  theme_bw()+ theme(legend.position = "top",axis.title.x = element_text(size = 20, vjust = -0.5),
        axis.text.y = element_text(size=18, angle = 0),axis.title.y = element_text(size=18, angle=90), 
        axis.text.x = element_text(size=20, angle=0), legend.title=element_text(size=18, angle=0),
        legend.text=element_text(size=16, angle = 0))

@@

>>>>

Fig_7 <- ggplot(as.data.frame(Alluvial),
       aes(y = N, axis1 = COD_DEPE2, axis2=TIPO_INST_3)) +
  geom_alluvium(aes(fill = COD_DEPE2), width = 1/12) +
  geom_stratum(width = 1/12, fill = "black", color = "grey") +
  geom_label(stat = "stratum", aes(label = after_stat(stratum))) +
  scale_x_discrete(limits = c("Dependence","Institution"), expand = c(.05, .05)) +
  scale_fill_brewer(type = "qual", palette = "Set1") + labs(y="Graduates", fill="Dependence") +
  theme_bw()+ theme(legend.position = "top",axis.title.x = element_text(size = 20, vjust = -0.5),
        axis.text.y = element_text(size=18, angle = 0),axis.title.y = element_text(size=18, angle=90), 
        axis.text.x = element_text(size=20, angle=0), legend.title=element_text(size=18, angle=0),
        legend.text=element_text(size=16, angle = 0))

@@

write.csv(coeficientes, file="coef.csv")
write.csv(p, file="p-value.csv")
